The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-14 document/ms.tex
words about comparisons

\setlength{\voffset}{0in}
\setlength{\hoffset}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{9in}
\setlength{\headheight}{0ex}
\setlength{\headsep}{\baselinestretch\baselineskip} % this is 2 lines in ``manuscript''
\setlength{\footnotesep}{0in}
\setlength{\topmargin}{-\headsep}

@@

\shorttitle{The population of long-period transiting exoplanets}
\shortauthors{Foreman-Mackey, Hogg, Morton, \etal}
% \submitted{Submitted to \textit{The Astrophysical Journal}}

@@

\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,\uw},
    David~W.~Hogg\altaffilmark{\scda,\nyu,\mpia,\cds},
    Timothy~D.~Morton\altaffilmark{\princeton},
    Bernhard~Sch\"olkopf\altaffilmark{\mpis},
    Eric~Agol\altaffilmark{\uw},
    and others
}

@@

>>>>

\setlength{\voffset}{0in}
\setlength{\hoffset}{0in}
\setlength{\textwidth}{6in}
\setlength{\textheight}{9in}
\setlength{\headheight}{0ex}
\setlength{\headsep}{\baselinestretch\baselineskip} % this is 2 lines in ``manuscript''
\setlength{\footnotesep}{0in}
\setlength{\topmargin}{-\headsep}
\setlength{\oddsidemargin}{0.25in}
\setlength{\evensidemargin}{0.25in}

@@

\shorttitle{The population of long-period transiting exoplanets}
\shortauthors{Foreman-Mackey, Morton, Hogg, \etal}
% \submitted{Submitted to \textit{The Astrophysical Journal}}

@@

\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,\uw},
    Timothy~D.~Morton\altaffilmark{\princeton},
    David~W.~Hogg\altaffilmark{\scda,\nyu,\mpia,\cds},
    Eric~Agol\altaffilmark{\uw},
    Bernhard~Sch\"olkopf\altaffilmark{\mpis},
    and others
}

@@

The population of long-period planets has been previously studied using radial
velocity, microlensing, and direct imaging surveys.
These methods all measure the occurrence rate in units of mass and semi-major
axis instead of radius and period.
Using the transit method, we do not directly measure the mass of the planet.
Instead, we must rely on a mass--radius relationship constructed using
exoplanets with both mass and radius measurements \citep[for
example]{Weiss:2014, Wolfgang:2016, Chen:2016} to predict the expected masses
of the transiting planets.

A detailed discussion of the systematic effects introduced by the use of a
mass--radius relationship is beyond the scope of this \paper\ but it is worth
noting that all published relationships are based on exoplanets much closer to
their host star than any of the candidates discussed here.

We find that the mean occurrence rate density in the range $0.01\,M_\mathrm{J}
\le M < 20\,M_\mathrm{J}$ and $1.5\unit{au} \le a < 9\unit{au}$ is
\begin{eqnarray}\eqlabel{massocc}
\frac{\dd^2 N}{\dd\ln M\,\dd\ln a} &=& \massocc
\end{eqnarray}
where $N$ is the expected number of planets per G/K dwarf.
The uncertainty in \eq{massocc} does not take into account the uncertainties
in the semi-major axis or mass estimates or any systematic noise in the
mass--radius relationship.
Therefore, the specific result should be taken with the appropriate grain of
salt but a result in this parameter space eases qualitative comparison with
occurrence rates measured using different methods.
